---
title: "Alcohol vs Seat choice"
author: "Leah Riganyan"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??



## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
   
The plots look as though there is a difference between amount of alcohol consumed, mainly that the back seats will consume much more than the middle and front seats, who are nearly equal in amount.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
   
As hypothesized, the median for the back seats is at a 4. The front seats are at 0, and the middle at 1. On average the 
people in the back will drink ~9 drinks, three time more than the middle, and nine times more than front. A statistical difference looks likely.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
   
If there wasn't a difference between all the seats and their alcohol consumption, then the likelihood that this result would happen is .000116.

## Tukey Test

```{r}
plot(TukeyHSD(model1))
```
   
This test shows us there's not a difference between middle and front seats. The difference stems from the back seats, whose confidence interval doesn't cross the 0 line in any other seat position. 


## Conclusions
   
We can conclude from these results that people who sit in the back are far more likely to consume copious amounts of alcohol than the middle or front seats. The difference between the front seats and the middle seats are 1-3 drinks, while the difference between the back seats differ by 6-9.
